Stat 400 Project

### 2021-12-04 Stat 400 proj.Rmd
Created new columns for incubation and recovery time and assign each new infection one in the infection status function.

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  return(df)
}

@@

#Function for getting updated coordinates
update_coords <- function(og_df, delta_df){
  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=3)
  new_df <- data.frame(new_mx)
  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
  new_df[,3] <- og_df[,3]
  colnames(new_df) <- c('x', 'y', 'subjects')

@@

  #store new infection status
  new_status <- rep(NA, nrow(current_non_infected))
  newly_infected <- NULL

@@

      if(d <= crucial_distance){
        new_status[j] <- 'I'
        newly_infected <- c(newly_infected, j)
      }
      else{
        new_status[j] <- 'S'
      }
    }
  }

  current_non_infected[newly_infected, 3] <- 'I'
  new_state <- rbind(current_infected, current_non_infected)

  # new_state <- c(new_status, current_infected[,3])
  return(new_state)
}

>>>>

  #Create null incubation and recovery time columns
  inc_time <- rep(NA, num_subjects)
  rec_time <- rep(NA, num_subjects)

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, inc_time, rec_time))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  colnames(df)[4] <- 'inc_time'
  colnames(df)[5] <- 'rec_time'
  return(df)
}

@@

#Function for getting updated coordinates
update_coords <- function(og_df, delta_df){
  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
  new_df <- data.frame(new_mx)
  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
  new_df[,3] <- og_df[,3]
  new_df[,4] <- og_df[,4]
  new_df[,5] <- og_df[,5]
  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')

@@

  #store vector of newly infecteds
  newly_infected <- NULL

@@

      if(d <= crucial_distance){
        newly_infected <- c(newly_infected, j)
      }
    }
  }

  current_non_infected[newly_infected, 3] <- 'I'
  #Give an incubation time
  current_non_infected[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 14)

  #Give a recovery time
  current_non_infected[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)

  new_state <- rbind(current_infected, current_non_infected)
  return(new_state)
}
